---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# xtensorrr

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

The goal of xtensorrr is to bundle all of the required headers of `xtensor`
and `xtl` into one package, along with the headers of `xtensor-r`, so you
can get started working with the headers right away, without having to 
worry about the `cmake` setup that `xtensor` (for good reason) uses.

Below we provide a few examples.

## Installation

``` r
devtools::install_github("DavisVaughan/xtensorrr")
```

## Example

```{r}
devtools::load_all()
```

Just get a 2x2 numeric matrix back
from an `xarray<double>`. There is some
dynamic sizing happening here

```{r}
two_by_two_rarray()
```

Just get a 2x2 numeric matrix back
from an xtensor<double, 2>
you have to be more explicit about
sizing here

```{r}
two_by_two_rtensor()
```

Add 1 to an R object
Using xarray means the dimensions are
determined dynamically

```{r}
plus_one(c(1, 2))

plus_one(matrix(c(1, 2)))

plus_one(array(1, dim = c(2, 2, 2)))
```

```{r}
# Interestingly, I think ALTREP breaks some of this
plus_one(1:5)

plus_one(1:5 + 1) # <- this is fine
```

